---
title: "Corona Virus Report"
author:
- familyname: Effendy
  othernames: Jimmy
  address: Monash Universty
  email: jef0001@student.monash.edu
  correspondingauthor: true
  qualifications:  B.Com
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r global, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(lubridate)
```



\section*{Country Italy and USA}

```{r covid-ita-usa, message = FALSE}
ita_usa <- read_csv(here::here("Data/worldwidecases.csv")) %>% 
  filter(countryterritoryCode %in% c("ITA", "USA"),
         year == "2020")
```

```{r cases-plot, warning = FALSE, fig.cap = "2020 COVID-19 Cases in Italy and USA"}
ita_usa %>% filter(month != 5) %>% 
  group_by(countryterritoryCode, month) %>% 
  summarise(total_cases = sum(cases)) %>% 
  ggplot(aes(x = month,
             y = total_cases,
             color = countryterritoryCode)) +
  geom_line()
```

Figure \@ref(fig:cases-plot) reflects the number of COVID-19 cases in Italy and USA from January to May 2020. The total number of cases are reflected in the y axis, and the x axis represents the period (month). It is reflected in the figure that COVID-19 cases did not start in Italy and USA until March where there was no significant difference between the two countries. There was a slight increase in COVID-19 cases in April in Italy. However, the number of cases in the US rose significantly in April. By the end of April, the number of cases in the US is approximately four times larger in comparison to Italy. According to [@vox] the number of COVID-19 cases in the US make up approximately a third of the world's cases.

\clearpage


```{r death-table, warning = FALSE}
ita_usa %>% select(countriesAndTerritories, dateRep, deaths) %>% 
  arrange(-deaths) %>% 
  head(5) %>% 
  kable(caption = "Top 5 Largest Number of Daily Deaths in Italy and USA") %>% 
  kable_styling(bootstrap_options = c("striped","hover"))
```

Table \@ref(tab:death-table) shows the top 5 largest daily in COVID-19 related deaths in Italy and USA. The table shows that the 5 largest amount of deaths occured in one day happened in the US. These mostly happened in the third and fourth week of April. The highest amount of daily deaths occured on the 16th of April, where 4,928 lose their lives.The second highest occured on the same week on the 18th of April with 3,770 number of deaths.

\section*{Country XX2 and YY2}
This section would do some analysis on China and Japan.

# read data

```{r read-data} 
selected_countries <- c("CHN", "JPN")
chn_jpn <- read_csv(here::here("Data/worldwidecases.csv")) %>% 
  filter(countryterritoryCode %in% selected_countries)
```

```{r tab1, echo = FALSE, tab.align = 'center', tab.cap = "Total cases and deaths in each country"}
cases <- chn_jpn %>% 
  group_by(countryterritoryCode) %>% 
  summarise(total_cases = sum(cases), 
            total_deaths = sum(deaths))
kable(cases) %>% 
  kable_styling(latex_options = c("striped", "hold_position"))
```

Table \@ref(tab:tab1) shows the total cases and deaths of COVID-19 in China and Japan from December 2019 to May 2020.

```{r fig1, echo = FALSE, fig.align = 'center', fig.cap = "Cases by time"}
library(lubridate)
library(plotly)
chn_jpn %>% 
  mutate(date = dmy(dateRep)) %>% 
  ggplot(aes(x = date, y = cases, group = countryterritoryCode)) + 
  geom_line() + 
  facet_wrap(~countryterritoryCode) 
ggplotly()

```


\@ref(fig:fig1) Shows the trend of cases reported every day in China and Japan. 
For China, there is a large increase from February 12 to February 13. The reason is that 13,332 of these 15141 new cases are clinically (rather than laboratory) confirmed cases, reported for the first time as an effect of a change in how cases are diagnosed and reported in Hubei province starting on February 12. See more information [here](https://www.worldometers.info/coronavirus/how-to-interpret-feb-12-case-surge/). If we ignore this outlier, there's an increasing trend from January 18 to February 5, and then the count of cases decreases till May. It can be seen that for China, the large-scale outbreak of the COVID-19 occurred between the end of January and the beginning of March.
For Japan, the peak of cases appeared in April 12 with a count of 1401. And the large-scale outbreak of the COVID-19 occurred between the end of March.


\section*{Country XX3 and YY3}



